\cvsection{Experience}
\begin{cventries}
  \cventry
    {Tech Lead, Technical Analyst.}
    {AKTrea Solutions private limited}
    {Chennai, India}
    {Jun. 2013 - Dec. 2014}
    {
      \begin{cvitems}
        \item[] {\textbf {Technologies used : ASP.NET, JavaScript/jQuery, MySQL, Android, Git, JIRA.} }
        \item {Performed version control using BitBucket and used various software development methodologies. }
        \item {Implemented a CRUD system using Entity framework in ASP.NET and created a WebAPI to send response based on the request. }
        %\item {Helped design a WebAPI such that it sends out scores based on the HTTP requests.}
        \item {Handled the tasks of designing, developing and maintaining optimized databases.}
        \item {Programmed and implemented a die based financial game with rules and logic using ASP.NET.}
        \item {Built the admin module for various games where you can add, maintain user records.}
        \item {Re-designed and developed web pages using Bootstrap and other CSS frameworks.}
        \item {Incorporated the novels "The League" and "Doosra" into two separate Android applications.}
      \end{cvitems}
    }
 
 
    \cventry
    {Junior Android Developer}
    {Ascenteq Info Solutions}
    {Chennai, India}
    {Feb. 2013 - Jun. 2013}
    {
        \begin{cvitems}
%            \item {Designed and built advanced applications for the Android platform.}
\item[]{\textbf {Technology used : Android.}}
            \item {Gained experience in developing a taxi booking android application "NTL Driver" using Google maps API.}
        \end{cvitems}
    }
    

\end{cventries}
